%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{hidelinks}

\usepackage[utf8x]{inputenc}

% Increase text height
\textheight=700pt

\newenvironment{absolutelynopagebreak}
  {\par\nobreak\vfil\penalty0\vfilneg
   \vtop\bgroup}
  {\par\xdef\tpd{\the\prevdepth}\egroup
   \prevdepth=\tpd}

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Konstantinos Kallas}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

% \address{Mpoumpoulinas 27 \\Dionisos, Greece, 14576\\\\Address 1 line 3}
% \address{Address 2 line 1\\Address 2 line 2\\Address 2 line 3}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{Contact} 
%% Address: Mpoumpoulinas 27, Dionisos, Greece, 14576 \\
%% Phone: +30 6957814666 \\
Email: \href{mailto:kallas@seas.upenn.edu}{kallas@seas.upenn.edu} -- Website: \href{https://angelhof.github.io/}{angelhof.github.io}
%% Github: \href{https://github.com/angelhof}{angelhof} \\

\section{Research}
The goal of my research is to enable the development of high-performance applications 
with robust correctness guarantees. 
% 
To achieve this goal, I build practical programmable software systems that target realistic workloads in widely-used environments. 
% 
I build my systems on solid foundations using formal specifications and techniques drawn from programming languages, compilers, and formal methods.

\section{Contents}

\hyperlink{sec:education}{\textbf{Education}},
\hyperlink{sec:employment}{\textbf{Employment}},
\hyperlink{sec:honors}{\textbf{Honors and Awards}},
\hyperlink{sec:publications}{\textbf{Publications}},
\hyperlink{sec:software}{\textbf{Software}},
\hyperlink{sec:press}{\textbf{Selected Press}},
\hyperlink{sec:mentoring}{\textbf{Research Mentoring}},
\hyperlink{sec:outreach}{\textbf{Outreach}},
\hyperlink{sec:service}{\textbf{Service}},
\hyperlink{sec:teaching}{\textbf{Teaching}},
\hyperlink{sec:talks}{\textbf{Invited Talks}},
\hyperlink{sec:references}{\textbf{References}}

\section{Education}

% HACK!! Hack to have links to sections, nothing else seems to work :( If I put the hypertarget in the section it breaks the alignment.
\hypertarget{sec:education}{\textbf{University of Pennsylvania}} \hfill {\em September 2018 -- present}\\
Computer and Information Science, PhD student \\
Advisor: Prof. Rajeev Alur

% \textbf{Eighth Summer School on Formal Techniques} \hfill \mbox{\em May 2018}\\
% Menlo College, Atherton, CA \\
% Organised by SRI International

\textbf{National Technical University of Athens} \hfill \mbox{\em October 2012 -- February 2018}\\
Electrical and Computer Engineering, Diploma \\ %% \hfill {\em GPA: 8.37/10} \\
% Specialization: Computer Science \hfill {\em Major (Last 2 years) GPA: 9.05/10} \\
Thesis: \textit{``HiPErJiT: A Profile-Driven Just-in-Time Compiler for Erlang''} \\
Advisor: Prof. Kostis Sagonas 

% Removing for now. Doesn't feel relevant for job apps.
% \textbf{Universita degli Studi dell'Aquila} \hfill {\em February 2015 -- July 2015} \\
% Computer Science, Erasmus Mobility Program %% \hfill {\em GPA: 9.4/10} \\
% Selected Courses: Programming Languages, Cryptography, and Software Engineering

% \textbf{Dionisos 1st High School, Greece} \hfill {\em Graduation: July 2012} \\
% Greek Apolitirion, ranked first among 120 students \hfill {\em GPA: 19.4/20}



\section{Employment}

\hypertarget{sec:employment}{\textbf{Research Intern}} \hfill {\em Summer 2020} \\
Microsoft Research, Redmond, US \\
Internship in the RiSE group; advised by Sebastian Burckhardt. \\
Worked on Durable Functions, a programming model for serverless applications.

\textbf{Research Intern}  \hfill {\em Summer 2019} \\
Amazon Web Services, New York, US \\
Internship in the Automated Reasoning Group; advised by Daniel Schwartz-Narbonne. \\
Worked on the verification of critical C code.

% \textbf{Google Summer of Code Student}  \hfill {\em May 2017 - September 2017} \\
% Worked with BEAM Community to extend the \textit{ejabberd} open source project. \\
% Implemented support for the \textit{``Let's Encrypt'' ACME} certificate acquiring protocol.

\textbf{Big Data Application Developer}  \hfill {\em Summer 2016} \\
Everis, Barcelona, Spain \\
Internship at the Big Data Center of Excellence. \\
Developed Big Data Applications using tools in the Hadoop ecosystem.

\section{Honors and Awards}

\hypertarget{sec:honors}{\textbf{Morris and Dorothy Rubinoff Award}} \hfill {\em 2024} \\
Best Computer Science Ph.D. thesis at Penn.

\textbf{A.G. Leventis Foundation PhD Grant} \hfill {\em 2021-2023}

\textbf{ACM SRC Grand Finals} \hfill {\em 2021} \\
\textit{2nd place} among SRC winners across all ACM conferences.

\textbf{HotOS 2021 Distinguished Presentation Award} \hfill {\em 2021} \\
Awarded for ``Unix Shell Programming: The Next 50 Years''.

\textbf{EuroSys 2021 Best Paper Award} \hfill {\em 2021} \\
Awarded for ``PaSh: Light-touch Data-Parallel Shell Processing''.

\textbf{POPL Student Research Competition} \hfill {\em 2021} \\
\textit{1st place} at the graduate category of the research competition. \\
Presented work on a parallelizing JiT compiler for shell scripts. 

\textbf{Gerondelis Foundation PhD Award} \hfill {\em 2020}

% \textbf{Programming Competitions}  \hfill {\em 2015-2018} \\
% Participation in many programming competitions. Notable examples: \\
% ICFP Programming Contest 2018 (Lightning) \textit{10th out of 91 teams}, \\
% IEEE Xtreme 2017 \textit{Top 5\%} and \textit{3rd} in Greece, IEEE Xtreme 2016 \textit{Top 10\%}

% \textbf{Heterogenous Computing Student Challenge Certificate}  \hfill {\em 2017} \\
% HiPEAC CSW, Zagreb, Croatia \\
% Optimizing GPU implementation of the K-means algorithm (NTUA-team) \\
% Supervision: Prof. Georgios Goumas

% \textbf{EESTech Challenge}  \hfill {\em 2017} \\ 
% Supervised Machine Learning Hackathon \\
% \textit{Joint 1st place} among 40 teams.

% \textbf{The Great Moment of Education Scholarship from Eurobank EFG}  \hfill {\em 2012} \\ 
% Achieving the highest rank in national qualifications exams in Dionisos high school.

% \textbf{9th European Union Science Olympiad} \hfill {\em 2011} \\ 
% Team-based science competition in Biology, Chemistry, and Physics.\\
% \textit{1st place} in local round and \textit{3rd place} in  national round. 

% \textbf{Mathematical Competition, Hellenic Mathematical Society} \hfill {\em 2010} \\ 
% Mathematical competition for high school students. \\
% Distinction in the 1st and 2nd local round. 


\section{Publications}

\input{pubs.tex}

Notes: $^*$ indicates equal contribution.

\section{Software}

\textbf{try} (\href{https://github.com/binpash/try}{Github: binpash/try}) \\
A tool that lets you run a command and inspect its effects before committing them to your system.

\hypertarget{sec:software}{\textbf{PaSh}} (\href{https://github.com/binpash/pash}{Github: binpash/pash}) \\
A bolt-on system that automatically parallelizes arbitrary shell programs with theoretical and practical correctness guarantees. \\
{\em Hosted by the \href{https://www.linuxfoundation.org/press-release/linux-foundation-to-host-the-pash-project-accelerating-shell-scripting-with-automated-parallelization-for-industrial-use-cases/}{Linux Foundation}}.

\textbf{DiSh} (\href{https://github.com/binpash/dish}{Github: binpash/dish}) \\
A system that automatically scales out shell scripts that operate on files in HDFS.

\textbf{mucache} (\href{https://github.com/eniac/mucache}{Github: eniac/mucache}) \\
A system that automatically adds and manages caches in microservice applications.

\textbf{mu2sls} (\href{https://github.com/eniac/mu2sls}{Github: eniac/mu2sls})  \\
A framework for correctly implementing stateful microservice applications on serverless using standard Python. 

\textbf{Flumina} (\href{https://github.com/angelhof/flumina}{Github: angelhof/flumina}) \\
A programming model and system for stateful distributed streaming computations.

\textbf{DiffStream} (\href{https://github.com/fniksic/diffstream}{Github: fniksic/diffstream}) \\
A differential testing library for stream processing applications in Apache Flink.

\section{Selected Press}

\hypertarget{sec:press}{\textbf{Practically Correct, Just-in-Time Shell Script Parallelization}} (\href{https://disseminatepodcast.podcastpage.io/episode/konstantinos-kallas-practically-correct-just-in-time-shell-script-parallelization-20}{link}) \\
Disseminate Podcast Episode 20, hosted by Jack Waudby. January 2023.

\textbf{Faster computing results without fear of errors} (\href{https://news.mit.edu/2022/faster-unix-computing-program-0607}{link}) \\
MIT News Article, written by Adam Zewe. June 2022.

\textbf{The PaSh Project -- Advancing the Unix Philosophy One Step Further} (\href{https://www.i-programmer.info/news/90-tools/14990-the-pash-project-advancing-the-unix-philosophy-one-step-further.html}{link}) \\
I-Programmer News Article, written by Nikos Vaggalis. November 2021.

\textbf{Linux Foundation to Host the PaSh Project, Accelerating Shell Scripting with Automated Parallelization for Industrial Use Cases} (\href{https://www.linuxfoundation.org/press/press-release/linux-foundation-to-host-the-pash-project-accelerating-shell-scripting-with-automated-parallelization-for-industrial-use-cases}{link}) \\
Linux Foundation Press Release, written by Kristin OConnell. September 2021.

% hackernews?

% \textbf{The Future of the Shell, Part 1} (\href{https://www.micahlerner.com/2021/07/14/unix-shell-programming-the-next-50-years.html}{link}) \\
% Blogpost by Micah Lerner. July 2021.


\section{Research Mentoring}

\hypertarget{sec:mentoring}{\textbf{Mayank Keoliya}} (UPenn, PhD) \hfill {\em 2023 -- present} \\
LLMs for Unix command specification.

\textbf{Dimitra Leventi} (NTUA, BSc) \hfill {\em 2023 -- present} \\
Characterization of shell workloads and development of a benchmark suite.

\textbf{Nikos Pagonas} (NTUA, BSc) \hfill {\em 2023 -- present} \\
Design and development of a serverless shell.

\textbf{Spyros Pavlatos} (UPenn, PhD) \hfill {\em 2022 -- present} \\
Development of correctness criteria for microservice applications.

\textbf{Akis Giannoukos} (UPenn, PhD) \hfill {\em 2022 -- present} \\
Overload control for microservice applications.

\textbf{Giorgos Liargovas} (AUEB, BSc) \hfill {\em 2022 -- present} \\
Out-of-order execution of shell scripts (paper at HotOS 2023).

\textbf{Tianyu (Ezri) Zhu} (Stevens, BSc) \hfill {\em 2022 -- present} \\
Design and development of \texttt{try}, a lightweight isolation tool for Linux (over 4k stars on \href{https://github.com/binpash/try}{Github}).

\textbf{Jiali Xing} (UPenn, PhD) \hfill {\em 2021 -- present} \\
Overload control for microservice applications (paper at HotNets 2021).

\textbf{Tammam Mustafa} (MIT, BSc $\rightarrow$ Google) \hfill {\em 2021 -- 2023} \\
Design and development of DiSh (papers at OSDI 2022 and NSDI 2023).

\textbf{Achilles Benetopoulos} (NTUA, BSc $\rightarrow$ UCSC, PhD) \hfill {\em 2019 -- 2021} \\
Development of PaSh's runtime and benchmarking of shell programs (paper at EuroSys 2021). 

\textbf{Lazar Cvetkovic} (University of Belgrade, BSc $\rightarrow$ ETH, PhD) \hfill {\em 2019 -- 2021} \\
Specification framework for POSIX and GNU Coreutils commands (paper at EuroSys 2021). 


\section{Outreach}

\hypertarget{sec:outreach}{\textbf{CS PhD MentoRes}}  \hfill {\em 2021 -- present} \\
Co-organizer of mentoring initiative for students that are interested in applying for PhD programs in CS but lack adequate resources. We have provided mentoring and resources to more than 40 students since the initiative's start.

\textbf{SIGPLAN-M}  \hfill {\em 2021 -- present} \\
Participating mentor for students in the programming languages community.

\textbf{SOSP Mentoring}  \hfill {\em 2023} \\
Student mentor in SOSP 2023.

\section{Service}

\hypertarget{sec:service}{\textbf{POPL 2023 Student Volunteer Co-Chair}}  \hfill {\em 2023}

\textbf{OOPSLA 2023 External Review and Artifact Evaluation Committee}  \hfill {\em 2023}

\textbf{POPL 2022 Student Volunteer Co-Chair}  \hfill {\em 2022}

\textbf{HotOS 2021 Co-organizer of a panel on the future of the shell} (\href{https://fut-shell.github.io/}{link})  \hfill {\em 2021}

\textbf{VMCAI 2021 Artifact Evaluation Committee}  \hfill {\em 2021}

\textbf{POPL 2020 External Reviewer}  \hfill {\em 2020}

\section{Teaching}

\hypertarget{sec:teaching}{\textbf{Teaching Assistant}}  \hfill {\em Fall 2021} \\
Institution: University of Pennsylvania \\
Course: \textit{Computer-Aided Verification}, Graduate level \\
Professor: Rajeev Alur

\textbf{Teaching Assistant}  \hfill {\em Fall 2019} \\
Institution: University of Pennsylvania \\
Course: \textit{Software Foundations}, Graduate level \\
Professor: Benjamin Pierce

\textbf{Lab Assistant}  \hfill {\em Fall 2017} \\
Institution: National Technical University of Athens \\
Course: \textit{Introduction to Programming}, Undergraduate level \\
Professors: S. Zachos, N. Papaspyrou, V. Kantere, and P. Potikas


\section{Invited Talks}

\input{talks.tex}

\section{References}

\hypertarget{sec:references}{\textbf{Rajeev Alur}}\\
Zisman Family Professor, Department of Computer and Information Science, University of Pennsylvania

\textbf{Sebastian Burckhardt}\\
Senior Principal Researcher, Microsoft Research

\textbf{Vincent Liu}\\
Assistant Professor, Department of Computer and Information Science, University of Pennsylvania

\textbf{Nikos Vasilakis}\\
Assistant Professor, Department of Computer Science, Brown University

\textbf{Keith Winstein}\\
Associate Professor, Department of Computer Science, Stanford University


% \section{Languages}

% \textbf{Greek} (Native), \textbf{English} (C2), \textbf{Italian} (C1), \textbf{German} (B2)


\end{resume}
\end{document}
