\begin{minipage}{\textwidth}
\textbf{Mucache: a General Framework for Caching in Microservice Graphs}. \\
Haoran Zhang$^*$, Konstantinos Kallas$^*$, Spyros Pavlatos, Rajeev Alur, Sebastian Angel, and Vincent Liu. \\
\emph{In submission}.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{DiSh: Dynamic Shell-Script Distribution}. \\
Tammam Mustafa, Konstantinos Kallas, Pratyush Das, and Nikos Vasilakis. \\
20th USENIX Symposium on Networked Systems Design and Implementation (NSDI 23), pp. 341-356.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Executing Microservice Applications on Serverless, Correctly}. \\
Konstantinos Kallas$^*$, Haoran Zhang$^*$, Rajeev Alur, Sebastian Angel, and Vincent Liu. \\
Proceedings of the ACM on Programming Languages (POPL 2023), pp. 367-395.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Executing Shell Scripts in the Wrong Order, Correctly}. \\
Georgios Liargkovas, Konstantinos Kallas, Michael Greenberg, and Nikos Vasilakis. \\
Proceedings of the 19th Workshop on Hot Topics in Operating Systems (HotOS 23), pp. 103-109.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Practically Correct, Just-in-Time Shell Script Parallelization}. \\
Konstantinos Kallas, Tammam Mustafa, Jan Bielak, Dimitris Karnikis, Thurston Dang, Michael Greenberg, and Nikos Vasilakis. \\
16th USENIX Symposium on Operating Systems Design and Implementation (OSDI 22), pp. 769-785.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Netherite: Efficient Execution of Serverless Workflows}. \\
Sebastian Burckhardt, Badrish Chandramouli, Chris Gillum, David Justo, Konstantinos Kallas, Connor McMahon, Christopher S. Meiklejohn, and Xiangfeng Zhu. \\
Proceedings of the VLDB Endowment 15 (VLDB 2022), pp. 1591-1604.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Stream Processing with Dependency-Guided Synchronization}. \\
Konstantinos Kallas$^*$, Filip Niksic$^*$, Caleb Stanford$^*$, and Rajeev Alur. \\
Proceedings of the 27th ACM SIGPLAN Symposium on Principles and Practice of Parallel Programming (PPoPP 2022), pp. 1-16.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{PaSh: Light-touch Data-Parallel Shell Processing}. \\
Nikos Vasilakis$^*$, Konstantinos Kallas$^*$, Konstantinos Mamouras, Achilleas Benetopoulos, and Lazar M. Cvetković. \\
Proceedings of the Sixteenth European Conference on Computer Systems (EuroSys 2021), pp. 49-66.\\
    \emph{Best Paper Award.}
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Durable Functions: Semantics for Stateful Serverless}. \\
Sebastian Burckhardt, Chris Gillum, David Justo, Konstantinos Kallas, Connor McMahon, and Christopher S. Meiklejohn. \\
Proceedings of the ACM on Programming Languages (OOPSLA 2021), pp. 1-27.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{An Order-aware Dataflow Model for Parallel Unix Pipelines}. \\
Shivam Handa$^*$, Konstantinos Kallas$^*$, Nikos Vasilakis$^*$, and Martin Rinard. \\
Proceedings of the ACM on Programming Languages (ICFP 2021), pp. 1-28.
\end{minipage}    

\begin{minipage}{\textwidth}
\textbf{Unix Shell Programming: The Next 50 Years}. \\
Michael Greenberg$^*$, Konstantinos Kallas$^*$, and Nikos Vasilakis$^*$. \\
Proceedings of the Workshop on Hot Topics in Operating Systems (HotOS 2021), pp. 104-111. \\
    \emph{Distinguished Presentation Award.}
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Charon: A Framework for Microservice Overload Control}. \\
Jiali Xing, Max Demoulin, Konstantinos Kallas, and Benjamin C. Lee. \\
Proceedings of the 18th ACM Workshop on Hot Topics in Networks (HotNets 2021), pp. 213-220.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Synchronization Schemas}. \\
Rajeev Alur, Phillip Hillard, Zachary G. Ives, Konstantinos Kallas, Konstantinos Mamouras, Filip Niksic, Caleb Stanford, Val Tannen, and Anton Xue. \\
Invited Paper at Proceedings of the 40th Symposium on Principles of Database Systems (PODS 2021), pp. 1-18.
\end{minipage}

% \begin{minipage}{\textwidth}
% \textbf{The Future of the Shell: Unix and Beyond}. \\
% Michael Greenberg$^*$, Konstantinos Kallas$^*$, and Nikos Vasilakis$^*$. \\
% Panel at the Workshop on Hot Topics in Operating Systems (HotOS 2021).
% \end{minipage}


\begin{minipage}{\textwidth}
\textbf{Preventing Dynamic Library Compromise on Node.js via RWX-Based Privilege Reduction}. \\
Nikos Vasilakis, Cristian-Alexandru Staicu, Grigoris Ntousakis, Konstantinos Kallas, Ben Karel, André DeHon, and Michael Pradel. \\
Proceedings of the ACM SIGSAC Conference on Computer and Communications Security (CCS'21), pp. 1821-1838.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{DiffStream: Differential Output Testing for Stream Processing Programs}. \\
Konstantinos Kallas$^*$, Filip Niksic$^*$, Caleb Stanford$^*$, and Rajeev Alur. \\
Proceedings of the ACM on Programming Languages (OOPSLA 2020), pp. 1-29.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Code-level model checking in the software development workflow at Amazon Web Services}. \\
Nathan Chong, Byron Cook, Jonathan Eidelman, Konstantinos Kallas, Kareem Khazem, Felipe R. Monteiro, Daniel Schwartz-Narbonne, Serdar Tasiran, Michael Tautschnig, and Mark R. Tuttle. \\
Software: Practice and Experience 2021, pp. 772-797.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Code-Level Model Checking in the Software Development Workflow}. \\
Nathan Chong, Byron Cook, Konstantinos Kallas, Kareem Khazem, Felipe R. Monteiro, Daniel Schwartz-Narbonne, Serdar Tasiran, Michael Tautschnig, and Mark R. Tuttle. \\
Proceedings of the ACM/IEEE 42st International Conference on Software Engineering: Software Engineering in Practice (ICSE-SEIP 2020), pp. 11-20.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Security Criteria for a Transparent Encryption Layer}. \\
Konstantinos Kallas, Clara Schneidewind, Benjamin C. Pierce, and Steve Zdancewic. \\
Workshop on Foundations of Computer Security (FCS 2019).
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{HiPErJiT: A Profile-Driven Just-in-Time Compiler for Erlang}. \\
Konstantinos Kallas and Konstantinos Sagonas. \\
Proceedings of the 30th Symposium on Implementation and Application of Functional Languages (IFL 2018), pp. 25-36.
\end{minipage}


