\begin{minipage}{\textwidth}
\hypertarget{sec:talks}{\textbf{PaSh: Practically Correct, Just-in-Time Shell Script Parallelization}}. \hfill {\em 2023}\\
Event: Invited lecture at Programming Language and Translators (COMS 4115) @ Columbia University.\\
  Host: Baishakhi Ray.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{PaSh: Practically Correct, Just-in-Time Shell Script Parallelization}. \hfill {\em 2023}\\
Event: Compute Seminar @ Technical University of Denmark (DTU).\\
 Host: Christian Gram Kalhauge.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Executing Microservices on Serverless, Correctly}. \hfill {\em 2023}\\
Event: Sysread Seminar @ Brown University.\\
 Host: Shriram Krishnamurthi.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Advancing the Serverless Paradigm}. \hfill {\em 2023}\\
Event: Invited Lecture at Systems Transforming Systems Course @ Brown University.\\
 Host: Nikos Vasilakis.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{PaSh: Practically Correct, Just-in-Time Shell Script Parallelization}. \hfill {\em 2023}\\
Event: Portland Programming Languages Seminar @ Portland State University.\\
 Host: Yao Li.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Executing Microservices on Serverless, Correctly}. \hfill {\em 2023}\\
Event: Programming Languages Seminar @ Harvard University.\\
 Host: Stephen Chong.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{PaSh: Practically Correct, Just-in-Time Shell Script Parallelization}. \hfill {\em 2023}\\
Event: CSLab Computing Systems Day @ National Technical University of Athens.\\
 Host: Georgios Goumas.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{PaSh: Practically Correct, Just-in-Time Shell Script Parallelization}. \hfill {\em 2022}\\
Event: Invited Lecture at Systems Transforming Systems Course @ Brown University.\\
 Host: Nikos Vasilakis.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{PaSh: Practically Correct, Just-in-Time Shell Script Parallelization}. \hfill {\em 2022}\\
Event: New England Programming Languages and Systems Symposium (NEPLS) @ Harvard University.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{PaSh: Practically Correct, Just-in-Time Shell Script Parallelization}. \hfill {\em 2022}\\
Event: New Jersey Programming Languages and Systems Seminar (NJPLS) @ Stevens University.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{PaSh: Practically Correct, Just-in-Time Shell Script Parallelization}. \hfill {\em 2022}\\
Event: Languages, Systems, and Data Group Seminar @ University of California Santa Cruz.\\
 Host: Lindsey Kuper.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{PaSh: Data-parallel shell scripting}. \hfill {\em 2022}\\
Event: Programming Research Laboratory Seminar @ Northeastern University (Virtual).\\
 Host: Arjun Guha.
\end{minipage}

\begin{minipage}{\textwidth}
\textbf{Flumina: Correct Distribution of Stateful Streaming Computations}. \hfill {\em 2020}\\
Event: Programming Languages Tea @ University of California San Diego.\\
 Host: Nadia Polikarpova.
\end{minipage}

% \begin{minipage}{\textwidth}
% \textbf{Flumina: Correct Distribution of Stateful Streaming Computations}. \hfill {\em 2019}\\
% Event: Athens Programming Languages Seminar @ National Technical University of Athens.\\
%  Host: Kostis Sagonas and Nikos Papaspirou.
% \end{minipage}

\begin{minipage}{\textwidth}
\textbf{HiPErJiT: A Profile-Driven Just-in-Time Compiler for Erlang}. \hfill {\em 2018}\\
Event: Athens Programming Languages Seminar @ National Technical University of Athens.\\
 Host: Kostis Sagonas and Nikos Papaspirou.
\end{minipage}


